---
title: "Guided Exercise 4"
author: "Zhirui Zhang, Aaron Guo"
date: "12/16/2021"
output: document
---

#The Case
You’ve been hired as the data science team for a liberal arts college. The college currently has an entering class of about 1,500 students, and collects 32 million in tuition revenue from those students. Recent increases in endowment income mean that the college can forego some of its tuition revenue in order to change the profile of admitted students.

#The college president and the board of trustees have two strategic goals:
1. Increase the average SAT score to 1300
2. Enroll at least 200 more students with incomes less than \$50,000
3. Don't allow tuition revenues from first-year students to drop to less than \$30 million
4. Keep the number of enrolled students between 1,450 and 1,550

#Your Job
Your job is to come up with a strategy to accomplish the administration’s goals.
You’ll need to incorporate the following elements into your two page memo for the president and the board of trustees.
Use conditional means to describe the probability of enrolling once admitted (yield) for different groups of students.
Create a model that accurately predicts the yield for admitted students. Describe the accuracy of this model and its key findings clearly.
Use the estimates from this model to adjust the current pricing strategy to induce other students to enroll, given the above constraints.Describe your approach clearly.
Predict the results of your change in pricing strategy.
There are lots of ways to accomplish all of the above. Remember that you need to write up your findings in a nice narrative, including charts and tables to make your key points. If you think there are some ethical implications to your approach, describe those as well.

#What to Submit
The document describing the above should be 2-4 pages. You can “knit” the document in html or pdf from Rmarkdown, or you can create a separate Word (google doc) or pdf document. You need to submit BOTH your Rmd file AND your written summary.

## Cleaning up
```{r}
# Clear variables
rm(list=ls())
# Clear all plots
graphics.off()
# Clear the console
cat("\014")
if (Sys.info()[[4]] == "AaronGuo-MacBookPro") {
  setwd("~/Programming/Vanderbilt/DS/DS1000/projects/DS-1000/")
}
```

## Set up
```{r}
library(modelr)
library(tidyverse)
library(tidymodels)
```

```{r}
ad<-read_rds("admit_data.rds")%>%
  ungroup()
```

## Part 1: Use conditional means to describe yield by different groups
```{r}
# by income
ad_income <- ad %>%
  mutate(income_decile = ntile(income, 10)) %>%
  group_by(income_decile) %>%
  summarize(min_income = min(income),
            pct_yield = mean(yield)) %>%
  ungroup()

ad_income

# ad %>%
#   ggplot(aes(x=income, y=yield)) +
#   geom_point() +
#   geom_smooth()
```

```{r}
# by sat
ad_sat <- ad %>%
  mutate(sat_decile = ntile(sat, 10)) %>%
  group_by(sat_decile) %>%
  summarize(min_sat = min(sat),
            pct_yield = mean(yield)) %>%
  ungroup()

ad_sat

# ad %>%
#   ggplot(aes(x=sat, y=yield)) +
#   geom_point() +
#   geom_smooth()
```

```{r}
# by gpa
ad_gpa <- ad %>%
  mutate(gpa_decile = ntile(gpa, 10)) %>%
  group_by(gpa_decile) %>%
  summarize(min_gpa = min(gpa),
            pct_yield = mean(yield)) %>%
  ungroup() 

ad_gpa
```

```{r}
# by visit
ad_visit <- ad %>%
  group_by(visit) %>%
  summarize(pct_yield = mean(yield)) %>%
  ungroup() 

ad_visit
```

```{r}
# by legacy
ad_legacy <- ad %>%
  group_by(legacy) %>%
  summarize(pct_yield = mean(yield)) %>%
  ungroup()

ad_legacy
```

```{r}
# by registered 
ad_registered <- ad %>%
  group_by(sent_scores) %>%
  summarize(pct_yield = mean(yield)) %>%
  ungroup()

ad_registered
```

```{r}
# by distance
ad_distance <- ad %>%
  mutate(log_distance_decile = ntile(log(distance), 10)) %>%
  group_by(log_distance_decile) %>%
  summarize(min_distance = min(distance),
            pct_yield = mean(yield)) %>%
  ungroup()

ad_distance
```

```{r}
# by net price
ad_net_price <- ad %>%
  mutate(net_price_decile = ntile(net_price, 10)) %>%
  group_by(net_price_decile) %>%
  summarize(min_price = min(net_price),
            pct_yield = mean(yield)) %>%
  ungroup()

ad_net_price

# ad %>%
#   ggplot(aes(x=net_price, y=yield)) +
#   geom_point() +
#   geom_smooth()
```


# ---------------- Part 2: Create a model to predict yield, and describe accuracy ----------------
##Data Wrangling
```{r}
ad<-ad%>%
  mutate(yield_f=as_factor(ifelse(yield==1,"Yes","No")))%>%
  mutate(yield_f=relevel(yield_f,ref="No"))%>%
    mutate(sat=sat/100,
         income=income/1000,
         distance=distance/1000,
         net_price=net_price/1000)
```
## Split Data 
```{r}
split_data_glm <- initial_split(ad)

ad_train_glm <- training(split_data_glm)

ad_test_glm <- testing(split_data_glm)
```

## Setting the Regression Model
```{r}
logit_mod<-logistic_reg()%>%
  set_engine("glm")%>%
  set_mode("classification")
```
Create formula and recipe:
```{r}
admit_formula <- as.formula(
                  "yield_f~
                          legacy+
                          visit+
                          registered+
                          sent_scores+
                          sat+
                          income+
                          gpa+
                          distance+
                          net_price")

admit_recipe<-recipe(admit_formula,ad)%>%
  step_log(distance)
```
add workflow:
```{r}
ad_wf<-workflow()%>%
  add_model(logit_mod)%>%
  add_recipe(admit_recipe)
```
fit the model:
```{r}
ad_result<-ad_wf%>%
  fit(ad_train_glm)
```
see the results:
```{r}
tidy(ad_result)
```
## Getting ROC
```{r}
# generate prediction
ad_wf_glm_pred <- ad_result %>%
  predict(ad_test_glm) %>%
  bind_cols(ad_test_glm)
```
```{r}
ad %>% 
  summarize(mean_yield = mean(yield))
```
```{r}
# accuracy
ad_wf_glm_pred %>%
  accuracy(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# sensitivity
ad_wf_glm_pred %>%
  sens(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# specificity
ad_wf_glm_pred %>%
  spec(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# ROC curve
ad_wf_glm_roc <- ad_result %>%
  predict(ad_test_glm, type="prob") %>%
  bind_cols(ad_test_glm)
```
```{r}
ad_wf_glm_roc %>%
  roc_curve(truth=yield_f, .estimate=.pred_Yes, event_level="second") %>%
  autoplot()
```
```{r}
ad_wf_glm_roc %>%
  roc_auc(truth=yield_f, .estimate=.pred_Yes, event_level="second")

```

##Getting the baselines
The average SAT score: 1225
```{r}
ad%>%
  filter(yield==1)%>% #only focus on students that actually showed up
  summarize(mean(sat) * 100)
```
Number of currently enrolled students who come from families that make less than $50,000 a year: 77; while there are 341 low-income students in total
- We did not capture 264 of these students 
```{r}
ad%>%
  filter(yield==1,income<50)%>%
  count()

ad%>%
  filter(income<50)%>%
  count()
```
Amount of total revenue collected from first-year students:$30,674,149
```{r}
ad%>%
  filter(yield==1)%>%
  summarize(dollar(sum(net_price) * 1000))
```
Number of students currently yield: 1466
```{r}
ad%>%
  filter(yield==1)%>%
  count()
```

##Changing Policies
```{r}
# generate prediction from our model
ad_pred <- ad_result%>%
  predict(ad)%>%
  bind_cols(ad)

# check predicted enrollment based on whether SAT is higher than 1300
ad_pred %>%
  group_by(sat >= 13, .pred_class)%>%
  count()
```
```{r}
# ad_np%>%
#   filter(.pred_class=="Yes")%>%
#   summarize(mean(sat))
# ad_pred_1 <- ad_pred %>% 
#   filter(sat < 13 & .pred_class=="No")
# ad_pred_2 <- ad_pred %>%
#   filter(sat < 13 & .pred_class=="Yes")
# ad_pred_3 <- ad_pred %>%
#   filter(sat > 13 & .pred_class=="No")
# ad_predp_4 <- ad_pred %>%
#   filter(sat > 13 & .pred_class=="Yes")
# ad_pred_combined <- rbind(ad_pred_1, ad_pred_2, ad_pred_3)
ad_pred_filtered <- ad_pred %>%
  filter(sat >= 13 | .pred_class=="Yes") %>% #to have students who either yielded or have scores >=1300
  summarize(mean(sat * 100))
ad_pred_filtered
```

Changing our financial aid policy for students who have higher SAT scores, such that students with SAT score higher than 1300 could get a deduction of \$40k in their tuition for every 100 score they exceeded the threshold, while students with lower scores will be added \$5k for every 100 score.
```{r}
ad_np<-ad%>%
  mutate(net_price=ifelse(sat>=13.50, 
                              net_price - (sat-13)*30,
                              net_price - (sat-13)*20))
ad_np <- ad_np %>%
  mutate(net_price=ifelse(net_price<0,0,net_price)) #if anybody has a net price of 0, change it to 0, otherwise leave it as it is-> because we don't charge people negative tuition!

ad_np <- ad_np %>%
  mutate(net_price = ifelse(income <= 50, -28, net_price))

ad_np <- ad_np%>%
  mutate(net_price = ifelse(income >= 180, 50, net_price))
```

# Generate prediction for the new policy
```{r}
# generate predictions
ad_np<-ad_result%>%
  predict(ad_np)%>%
  bind_cols(ad_np)
```
```{r}
# calculate the total revenue to the school from students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(dollar(sum(net_price)*1000))
```
```{r}
# calculate the SAT average for students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(mean(sat)*100)
```
```{r}
# calculate how many students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  count()
```
```{r}
# calculate how many low income students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  filter(income<=50)%>%
  count()
```
We saw the mean sat score is increased to 1239, and the net price ($30,572,784) is still above the required level, while the number of students (1390) is within expected, with 27 low income student.

Add another policy: deduct $30k for students whose family income is below $50,000
```{r}
ad_np<-ad%>%
  mutate(net_price=ifelse(sat>=13, 
                              net_price - (sat-13)*40,
                              net_price - (sat-13)*5))%>%
  mutate(net_price=ifelse(income<=50, 
                              net_price - 30,
                              net_price))%>%
  mutate(net_price=ifelse(net_price<0,0,net_price)) #if anybody has a net price of 0, change it to 0, otherwise leave it as it is-> because we don't charge people negative tuition!
```
```{r}
ad_np<-ad_result%>%
  predict(ad_np)%>%
  bind_cols(ad_np)
```
```{r}
# calculate the total revenue to the school from students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(dollar(sum(net_price)*1000))
```
```{r}
# calculate the SAT average for students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(mean(sat)*100)
```
```{r}
# calculate how many students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  count()
```
```{r}
# calculate how many low income students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  filter(income<=50)%>%
  count()
```
We now have a total revenue of $30,275,183 (above expectation), an SAT average of 1237 (below expectation), a total number of enrollment of 1412 (below expectation), and 76 low income students (below expectation).

Add another policy: 
```{r}
ad_np<-ad%>%
  mutate(net_price=ifelse(sat>=13, 
                              net_price - (sat-13)*35,
                              net_price - (sat-13)*5))%>%
  mutate(net_price=ifelse(income<=50, #incentivize low income
                              net_price - 30,
                              net_price))%>%
  mutate(net_price=ifelse(income>=150, #for high income
                              net_price + 10,
                              net_price))%>%
  mutate(net_price=ifelse(gpa>=3.8, #gpa和yield也有positive correlation
                              net_price - (gpa-3.8)*10,
                              net_price))%>%
  mutate(net_price=ifelse(sent_scores==1,#sent scores和yield的correlation最强
                              net_price - 10,
                              net_price))%>%
  mutate(net_price=ifelse(net_price<0,0,net_price)) #if anybody has a net price of 0, change it to 0, otherwise leave it as it is-> because we don't charge people negative tuition!
```
```{r}
ad_np<-ad_result%>%
  predict(ad_np)%>%
  bind_cols(ad_np)
```
```{r}
# calculate the total revenue to the school from students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(dollar(sum(net_price)*1000))
```
```{r}
# calculate the SAT average for students now predicted to enroll
ad_np%>%
  filter(.pred_class=="Yes")%>%
  summarize(mean(sat)*100)
```
```{r}
# calculate how many students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  count()
```
```{r}
# calculate how many low income students are now predicted to enroll
ad_np %>%
  filter(.pred_class=="Yes") %>%
  filter(income<=50)%>%
  count()
```
We now have a total revenue of $32,838,519 (meet expectation, above original), an SAT average of 1234 (below expectation, above original), a total number of enrollment of 1458 (meet expectation), and 77 low income students (below expectation, same as original).



