## Cleaning up
```{r}
# Clear variables
rm(list=ls())
# Clear all plots
graphics.off()
# Clear the console
cat("\014")
if (Sys.info()[[4]] == "AaronGuo-MacBookPro") {
  setwd("~/Programming/Vanderbilt/DS/DS1000/projects/DS-1000/")
}
```

## Set up
```{r}
library(modelr)
library(tidyverse)
library(tidymodels)
```

```{r}
ad<-read_rds("admit_data.rds")%>%
  ungroup()
```


# Data Wrangling
```{r}
ad<-ad%>%
  mutate(yield_f=as_factor(ifelse(yield==1,"Yes","No")))%>%
  mutate(yield_f=relevel(yield_f,ref="No"))%>%
    mutate(sat=sat/100,
         income=income/1000,
         distance=distance/1000,
         net_price=net_price/1000)
```
# Filter out low-income students (income < $50,000)
```{r}
ad_lowincome <- ad %>%
  filter(income < 50000/1000)
```

# Split the data for analysis
```{r}
split_data_glm <- initial_split(ad_lowincome)

ad_train_glm <- training(split_data_glm)

ad_test_glm <- testing(split_data_glm)
```
# Logistical regression analysis
```{r}
logit_mod<-logistic_reg()%>%
  set_engine("glm")%>%
  set_mode("classification")

admit_formula <- as.formula(
                  "yield_f~
                          legacy+
                          visit+
                          registered+
                          sent_scores+
                          sat+
                          income+
                          gpa+
                          distance+
                          net_price")

admit_recipe<-recipe(admit_formula,ad)%>%
  step_log(distance)

ad_wf<-workflow()%>%
  add_model(logit_mod)%>%
  add_recipe(admit_recipe)

ad_result<-ad_wf%>%
  fit(ad_train_glm)

tidy(ad_result)
```

## Getting ROC
```{r}
# generate prediction
ad_wf_glm_pred <- ad_result %>%
  predict(ad_test_glm) %>%
  bind_cols(ad_test_glm)
```
```{r}
ad %>% 
  summarize(mean_yield = mean(yield))
```
```{r}
# accuracy
ad_wf_glm_pred %>%
  accuracy(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# sensitivity
ad_wf_glm_pred %>%
  sens(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# specificity
ad_wf_glm_pred %>%
  spec(truth=yield_f, estimate=.pred_class, event_level="second")
```
```{r}
# ROC curve
ad_wf_glm_roc <- ad_result %>%
  predict(ad_test_glm, type="prob") %>%
  bind_cols(ad_test_glm)
```
```{r}
ad_wf_glm_roc %>%
  roc_curve(truth=yield_f, .estimate=.pred_Yes, event_level="second") %>%
  autoplot()
```
```{r}
ad_wf_glm_roc %>%
  roc_auc(truth=yield_f, .estimate=.pred_Yes, event_level="second")

```

```{r}
# Extract results
ad_fit <- ad_result %>% extract_fit_parsnip()
```



# what if the net price is negative
```{r}
hypo_data <- ad_lowincome %>%
  # supply the mode (for each variable) of the entire dataset 
  data_grid(.model=ad_fit$fit,
            net_price = seq(from=-5, to=0, by=0.05))
```
```{r}
ad_negativeprice <- ad_result%>%
  predict(hypo_data,type="prob")%>%
  bind_cols(hypo_data)
```

```{r}
ad_lowincome %>%
  ggplot(aes(x=net_price, y=yield)) + 
  geom_point() +
  geom_smooth()
ad_negativeprice %>%
  ggplot(aes(x=net_price, y=.pred_Yes)) + 
  geom_point() +
  geom_smooth()
```